\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-22 paper.tex
revised Intrdouction to paper

Script is what Bitcoin uses to encode transactions over the network. It is purposefully restricted, and most notably lacks a mechanism for looping and guarantees termination. To properly learn the language and understand its semantics, one must read through the catalog of \textit{opcodes} (hex values used as operators) and analyze its C++ reference implementation.

As a postfix language written in sequences of bytes, Script is not an easy language to pick up and understand. It is even harder to assess the effect that proposed modifications to the language might have on the guarantees that it must provide. In the past, Script has been progressively restricted in response to discovered vulnerabilities in the language. The restrictions eliminated the vulnerabilities, at the cost of reducing the expressiveness of the language. It is not clear that all of the restrictions added were necessary to produce the desired end of securing the language. A formal description and eventually specification would help in such determinations, allowing more objective and precise decisions.

@@

Our proposed grammar, in constrast, unambiguously describes the behavior of Script, is easier to reason about than the C++ code, and can (hopefully eventually) serve as basis for further analytic work.

>>>>

Bitcoin is a fully decentralized payment system, the first practical decentralized solution to "the double spending problem." Bitcoin has in the years since its introduction grown to prominence, with dozens if not hundreds of crypto-currencies following in its wake. Bitcoin is generally the simplest and most-established of these, serving as the anchor currency, against which other crypto-currencies are valued.

There has been a great deal of research into different aspects of Bitcoin. One particularly central aspect has, however, been under-examined. The transactions so secured by the Bitcoin network are encoded in Script, a programming language tasked with determining the validity of a transaction.

Script, as with the the entirety of the Bitcoin protocol, lacks a formal specification. Rather, it is defined by the grammar and serialization implied by the reference implementation of Bitcoin. We set out to provide a formal description of the Script language and to demonstrate, with somewhat simple examples, how such a description might be useful in analyzing the properties of the language.

Script is purposefully restricted, most notably lacking a mechanism for looping or recursion, guaranteeing termination. A a stack-based language written with byte literals as program text and no formal specification to turn to, Script is not an easy language to pick up and understand. It is a similarly difficult task to analyze it's behavior without a formal grammar.

In the past, Script has been progressively restricted in response to discovered vulnerabilities in the language. The restrictions eliminated such vulnerabilities at the cost of reducing the expressiveness of the language. It is not clear that all of the restrictions added were entirely necessary to secure the language.

This is complicated by the lack of any sufficiently precise definition of security. It is our hope that a formal description and eventually specification of Script will aid the construction of framework for such determinations, allowing more objective and precise analysis of both current and proposed future forms of the language.

@@

Our proposed grammar, in constrast, unambiguously describes the behavior of Script, is easier to reason about the C++ code, and can (hopefully eventually) serve as basis for further analytic work.
